Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars

### 2018-03-16 main.tex
revisions through end of section 4, and added a reference

%mm3 {\bf New (addressing KVJ's comment to clarify how to interpret / what is target comparison point for our galaxy model:} 
We emphasize here that our model, with no initial stellar distribution, is not intended to reproduce the evolution of Leo P, which has formed stars continuously over cosmological timescales. In addition, the mass fractions for the individual metals we track are set to zero so that we follow only the evolution of metals self-consistently produced in the simulations. Otherwise, the galaxy chemical properties would be dominated by the somewhat arbitrary choice of initial abundances. In some ways this is similar to the first pollution of pristine gas in the early Universe, but we note that we cannot directly make this comparison as the environmental conditions and UVB properties were different at high redshift, and we explicitly ignore Pop III and Pop II stellar evolution. Instead, this work is intended as a numerical experiment to investigate how metal enrichment from ongoing star formation proceeds in a gas / dark matter environment similar to low mass halos at both low redshift and the early Universe. The subsequent metal enrichment from the stars in our simulation can be thought of as
%mm3
    tracking 
a change in abundances
%mm3 , or delta abundances, 
from arbitrary initial conditions. We 
%mm3
   will 
discuss how to make proper comparisons to observed stellar and gas abundance properties of dwarf galaxies in future work, where we investigate the abundance evolution of our simulations in more detail.

\section{Results}
\label{sec:results}
We present our initial results here, providing an overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the 500~Myr after the first star forms. Unless otherwise noted, $t = 0$ is defined as the time at which the first star particle forms, which is 43~Myr after the actual initialization of the simulation. The galaxy disk is defined as the fixed physical region within a cylindrical radius of 600~pc and $|z| < 200$~pc relative to the center of the galaxy. ISM properties are calculated considering only the gas contained within the disk of the galaxy. We include a resolution study in Appendix \ref{appendix:resolution_study},

@@

At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component. By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), \ion{H}{1} still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about $6 \times 10^5$ M$_{\odot}$, or roughly 17\%, of the total mass in the galaxy's disk. The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction increases over time to roughly 35-40\%; at this point, it is about equal with the \ion{H}{1} gas. This is because the total amount of mass in the disk decreases through feedback-driven winds, but the H$_2$ is preferentially retained. Small fluctuations in the H$_2$ mass correspond with small increases in the total stellar mass, as some small fraction of H$_2$ is converted into stars, and more is destroyed from the subsequent feedback. Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}. The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.

@@

The mass of the ISM in our dwarf galaxy is dominated by the CNM for the first 200~Myr of simulation time, as shown in the left panel of Figure~\ref{fig:ISM_evolution}. After this point, the molecular component dominates through the end of the simulation. Together, the CNM and molecular phases comprise $\sim 90\%$ of the total ISM mass, with the remaining mass dominated by the WNM. While the CNM has a negligible volume fraction, the WNM, WIM, and HIM each occupy roughly the same volume fraction. However, the frequent fluctuations in the HIM volume fraction mean that the WIM and WNM more consistently dominate the volume of the galaxy. Together, these figures better quantify the general properties observed in the panel plots in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.

These results are in contrast with those found for the more massive dwarf galaxy in \citet{Hu2016,Hu2017}. They find the mass and volume fraction of the ISM are nearly entirely dominated by warm gas (ionized and neutral), with cold gas having $\sim$ 10\% of the mass, and occupying negligible volume, and hot gas occupying $\sim$ 10\% of the volume, but having negligible mass. Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) by a large factor, and more hot gas (by volume fraction) by a factor of a few. The driver of these differences, which are likely somewhat related to differences in the dark matter halo potential, will be investigated in future work. {\bf We have compared our cooling curves to those used in \citep{Hu2017} (C. Hu, private communication) and found them to be comparable; though this could contribute to the differences, it is likely not the dominant source.}

@@

Interestingly, the v$_{\rm c}\sim$ 30 km s$^{-1}$ halos examined in \citet{Muratov2015} are more massive than the M$_{\rm vir} = 2.5\times 10^9$ M$_{\odot}$ halo examined here by a factor of a few. Using a fit provided in \citet{Muratov2015} to extrapolate and compare $\eta$ at fixed halo mass, one would expect mass loading factors on order of 100 at 0.25 R$_{\rm vir}$ for our dwarf galaxy, a factor of a few higher than what we find. These differences could be attributed to our lack of cosmological evolution in these isolated simulations, but ultimately requires a larger set of dwarf galaxy simulations to make a more robust comparison. We note, however, that our results are closer to the \citep{Muratov2015} results than those in \citet{Hu2016,Hu2017}, which find mass loading factors at 0.05 $R_{\rm vir}$ between 1 and 10 for a dwarf galaxy with M$_{\rm vir} = 10^{10}$ M$_{\odot}$, and therefore certainly have much smaller mass loading factors at 0.25 $R_{\rm vir}$.

@@

Detailed outflow properties, beyond outflow rates and mass loading factors, can help discriminate between the model dependent feedback physics included in galaxy simulations. In Figure~\ref{fig:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases. Half of the outflow, by mass, is at velocities below 40 km s$^{-1}$, with 75\% at velocities of 70 km s$^{-1}$ or below. This gas is dominated by the two warm gas phases, with the WNM dominating at lower velocities, and the WIM at higher velocities. The distribution has a very long tail out to and beyond 500~km~s$^{-1}$. The dominant launching mechanism in this simulation are SNe, generating a rapidly moving and volume-filling HIM, consistent with the results in \citet{Hu2016,Hu2017}. However, as shown, the HIM comprises very little of the outflow by mass. Most of the outflowing gas (by mass) comes from the warm phase, pushed out by the high pressure, fast moving HIM. Some of this warm gas certainly originates from adiabatically and radiatively cooled HIM, however. The amount of transfer between phases in the halo of our galaxy will be investigated in future work.

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{outflow_velocity_distribution}
\caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy. The outflowing material is multiphase, broken into WNM, WIM, and HIM. See Section~\ref{sec:phase} for definitions of these regimes. We note that WNM is often labeled simply as ``cold'', or gas below $T = 10^{4}$K. There is little to no outflowing mass in the CNM or molecular phases.}
\label{fig:outflow_velocity}
\end{figure}

@@

\subsubsection{Metal Enriched Outflows}
Dwarf galaxies efficiently, and preferentially, eject metals released in stellar feedback from their shallow potential wells \citep{MacLowFerrara1999,FerraraTolstoy2000}. This has been better quantified recently both observationally \citep[e.g.][]{Kirby2011-metals,Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Simpson2013,Angles-Alcazar2017,Muratov2017}. In the top panel of Fig.~\ref{fig:metal_evolution}, we give the metal mass loading factor for our galaxy over time, at the same radii as in Fig.~\ref{fig:mass_outflow}. The parameter used to quantify metal outflow efficiencies varies among works. Here, we define the metal mass loading factor as the metal outflow rate divided by the metal production rate, or
\begin{equation} \label{eq:eta-metal}
\eta_{\rm metal} = \frac{\dot{M}_{\rm metal}}{\rm{SFR} \times \frac{M_{\rm metal}}{M_{*}}},
\end{equation}
where $\dot{M}_{\rm metal}$ is the metal mass outflow rate, $M_{\rm metal}$ is the total mass in metals produced, and $M_{*}$ is the total mass in stars. We note the very large loading factors in the first 20~Myr are artificial, and a byproduct of the initial conditions. For half of the evolution, the inner three radii give $\eta_{\rm metal}$ below unity (around 0.6), but it increases at each radius, fluctuating around unity for the second half of the simulation. Recent simulations of outflows from a Milky Way type disk indicate typical $\eta_{\rm metal}$ comparable to our results, usually between 0.5 and 1 \citep{Li2017,Fielding2017}. \cite{Muratov2017} computes a slightly different quantity for their galaxies, the normalized metal outflow rate $\eta_{Z} = \dot{M}_{\rm metal}/{\rm SFR}$, finding values of about 0.02 at 0.25~$R_{\rm vir}$ regardless of galaxy circular velocity. Our galaxy is consistent with this value, with an average $\eta_Z = 0.015$, fluctuating between 0.007 and 0.02.

@@

\subsubsection{Differential Mixing of Elements Within the ISM}
\textbf{CHANGE: Simplified plot to just log(N/O) to make this less confusing and easier to interpret. Cleaned up text accordingly.}
It is important to understand how metals from each source of stellar yields enrich the ISM. Observations of more massive dwarf galaxies than those simulated here indicate fairly uniform radial gas-phase metallicity profiles, even beyond the stellar radius \citep[e.g.][]{Werk2011,Belfiore2017}. This requires that metal mixing and transport occur on hundred megayear timescales, much more rapidly than the gigayear timescale expected from assuming transport at the cold gas sound speed. Therefore, either metals are transported first through a hot phase with high sound speed, or through efficient turbulent mixing within the ISM \citep[e.g.][]{Tassis2008,YangKrumholz2012}. It remains uncertain how metal abundances vary in detail within these galaxies, beyond one-dimensional radial profiles, and whether or not abundance distributions depend on the metal species. It is even more unclear how metals are transported and distributed within ultrafaint dwarf galaxies, which generally host too few \ion{H}{1}I regions for a detailed examination.

@@

We demonstrate the power of our simulations, which capture a realistic ISM at high resolution with multiple feedback sources, by addressing these questions in Fig~\ref{fig:metal_slices}. The left two panels give the slices of number density (top right) and temperature (bottom right) in the mid-plane of a portion of our dwarf galaxy. These serve to guide the eye in the right panel, clearly indicating regions with dense, cold gas clouds ($n \sim 100~\rm{cm}^{-2}$, $T \lesssim 100~$K), warm, diffuse gas ($n\sim 0.1$~cm$^{-3}$, $T\sim 10^{4}$~K), and hot gas from a recent SN explosion ($T\sim10^{6}$~K). The left panel gives the abundance ratio of N to O throughout the ISM.

@@

The number density and temperature panels clearly show a multi-phase ISM: the CNM consists of cold filaments that connect dense clumps of molecular gas which are readily visible in both diagrams. Distinguishing the WNM and WIM is difficult, but the lower density regions between the cold filaments is dominated by these phases. Gas from a recent SN explosion is clearly visible as the hot (T~$\gtrsim 10^{6}$~K) and diffuse region in the top left corner. As shown in the left panel, log(N/O) varies significantly over this section of the ISM with notable differences across the various phases and ISM structures. As expected, O is overabundant throughout the ISM, most strongly in the region of recent SN enrichment (top left, dark purple region in log(N/O) / dark red in temperature). However, the relative abundance of N increases significantly in the warmer phases, reaching equipartition (white color in log(N/O)) in many patches throughout the ISM. There are three regions in particular that are overabundant in N (green color). These are sites of recent AGB winds that have yet to mix with the rest of the ISM.

@@

At our adopted metallicity, nitrogen is predominantly produced in AGB star winds, with very little production in core collapse SNe and winds from more massive stars. Therefore, nitrogen is injected into the ISM with significantly less energy ($v \sim 10$~km~s$^{-1}$) than elements produced in SNe, like oxygen, ($v\sim 10^3$~km~s$^{-1}$). Given the variations in Figure~\ref{fig:metal_slices}, the energetic differences between injection sources can drive abundance variations within the ISM of our dwarf galaxy. This suggests that metal mixing within the ISM (and also metal ejection from the ISM) is species dependent. A more detailed analysis is beyond the scope of this work, but we plan to investigate this point, and potential observational consequences for stellar abundances, in future work. 
% reference my other paper if it is ready-ish by the time I submit this one.

>>>>

%mm3 {\bf New (addressing KVJ's comment to clarify how to interpret / what is target comparison point for our galaxy model:} 
We emphasize here that our model, with no initial stellar distribution, is not intended to reproduce the evolution of Leo P, which has formed stars continuously over cosmological timescales. In addition, the mass fractions for the individual metals we track are set to zero so that we follow only the evolution of metals self-consistently produced in the simulations. Otherwise, the galaxy chemical properties would be dominated by the somewhat arbitrary choice of initial abundances. In some ways this is similar to the first pollution of pristine gas in the early Universe, but we note that we cannot directly make this comparison as the environmental conditions and UVB properties were different at high redshift, and we explicitly ignore Pop III and Pop II stellar evolution. Instead, this work is intended as a numerical experiment to investigate how metal enrichment from ongoing star formation proceeds in a gas / dark matter environment similar to low mass halos at both low redshift and the early Universe. The subsequent metal enrichment from the stars in our simulation can be thought of as
%mm3
    tracking 
a change in abundances
%mm3 , or delta abundances, 
from arbitrary initial conditions. We 
%mm3
   will 
discuss how to make proper comparisons to observed stellar and gas abundance properties of dwarf galaxies in future work, where we will investigate the abundance evolution of our simulations in more detail.

\section{Results}
\label{sec:results}
We present our initial results here, providing an overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the 500~Myr after the first 
%mm3
   new
star forms. Unless otherwise noted, $t = 0$ is defined as the time at which that first star particle forms, which is 43~Myr after the actual 
%mm3 initialization of the simulation
   beginning of the simulation run. 
The galaxy disk is defined as the fixed physical region within a cylindrical radius of 600~pc and vertical heigh $|z| < 200$~pc relative to the center of the galaxy. ISM properties are calculated considering only the gas contained within the disk of the galaxy. We include a resolution study in Appendix \ref{appendix:resolution_study}.

@@

At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component. By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), \ion{H}{1} still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about $6 \times 10^5$ M$_{\odot}$, or roughly 17\%, of the total 
%mm3 [confirm]
    gas 
mass in the galaxy's disk. The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction increases over time to roughly 35-40\%; at this point, it is about equal with the \ion{H}{1} gas. This is because the total amount of 
%mm3 mass 
    gas
in the disk decreases through feedback-driven winds, but the H$_2$ is preferentially retained. Small fluctuations in the H$_2$ mass correspond with small increases in the total stellar mass, as some small fraction of H$_2$ is converted into stars, and more is destroyed from the subsequent feedback. Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}. The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.

@@

The mass of the ISM in our dwarf galaxy is dominated by the CNM for the first 200~Myr of simulation time, as shown in the left panel of Figure~\ref{fig:ISM_evolution}. After this point, the molecular component
%mm3 dominates
   becomes equally or even somewhat more important 
through the end of the simulation. Together, the CNM and molecular phases comprise $\sim 90\%$ of the total ISM mass, with the remaining mass dominated by the WNM. While the CNM has a negligible volume fraction, the WNM, WIM, and HIM each occupy roughly the same volume fraction. However, the frequent fluctuations in the HIM volume fraction mean that the WIM and WNM more consistently dominate the volume of the galaxy. Together, these figures better quantify the general properties observed in the panel plots in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.

These results are in contrast with those found for the more massive dwarf galaxy modeled by \citet{Hu2016,Hu2017}. They find the mass and volume fraction of the ISM are nearly entirely dominated by warm gas (ionized and neutral), with cold gas having $\sim$ 10\% of the mass, and occupying negligible volume, and hot gas occupying $\sim$ 10\% of the volume, but having negligible mass. Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) by a large factor, and more hot gas (by volume fraction) by a factor of a few. The driver of these differences, which are likely somewhat related to differences in the dark matter halo potential, will be investigated in future work. {\bf We have compared our cooling curves to those used in \citep{Hu2017} (C. Hu, private communication) and found them to be comparable; though this could contribute to the differences, it is likely not the dominant source.}

@@

Interestingly, the v$_{\rm c}\sim$ 30 km s$^{-1}$ halos examined in \citet{Muratov2015} are more massive than the M$_{\rm vir} = 2.5\times 10^9$ M$_{\odot}$ halo examined here by a factor of a few. Using a fit provided in \citet{Muratov2015} to extrapolate and compare $\eta$ at fixed halo mass, one would expect mass loading factors on order of 100 at 0.25 R$_{\rm vir}$ for our dwarf galaxy, a factor of a few higher than what we find. These differences could be attributed to our lack of cosmological evolution in these isolated simulations, but ultimately requires a larger set of dwarf galaxy simulations to make a more robust comparison. We note, however, that our results are closer to the \citet{Muratov2015} results than those in \citet{Hu2016,Hu2017}, which find mass loading factors at 0.05 $R_{\rm vir}$ between 1 and 10 for a dwarf galaxy with M$_{\rm vir} = 10^{10}$ M$_{\odot}$, and therefore certainly have much smaller mass loading factors at 0.25 $R_{\rm vir}$.

@@

Detailed outflow properties, beyond outflow rates and mass loading factors, can help discriminate between the model dependent feedback physics included in galaxy simulations. In Figure~\ref{fig:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases. Half of the outflow, by mass, is at velocities below 40 km s$^{-1}$, with 75\% at velocities of 70 km s$^{-1}$ or below. This gas is dominated by the two warm gas phases, with the WNM dominating at lower velocities, and the WIM at higher velocities. The distribution has a very long tail out to and beyond 500~km~s$^{-1}$. The dominant launching mechanism in this simulation is SN feedback, which generates a rapidly moving and volume-filling HIM, consistent with the results in \citet{Hu2016,Hu2017}. However, as shown, the HIM comprises very little of the outflow by mass. Most of the outflowing gas (by mass) comes from the warm phase, pushed out by the high pressure, fast moving HIM. Some of this warm gas certainly originates from adiabatically and radiatively cooled HIM, however. The amount of transfer between phases in the halo of our galaxy will be investigated in future work.

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{outflow_velocity_distribution}
\caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy. The outflowing material is multiphase, broken into WNM, WIM, and HIM. See Section~\ref{sec:phase} for definitions of these regimes. We note that WNM is often labeled simply as ``cold'', or gas below $T = 10^{4}$~K. There is little to no outflowing mass in the CNM or molecular phases.}
\label{fig:outflow_velocity}
\end{figure}

@@

\subsubsection{Metal Enriched Outflows}
Dwarf galaxies efficiently, and preferentially, eject metals released in stellar feedback from their shallow potential wells \citep{MacLowFerrara1999,FerraraTolstoy2000}. This has been better quantified recently both observationally \citep[e.g.][]{Kirby2011-metals,Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Simpson2013,Angles-Alcazar2017,Muratov2017}. In the top panel of Fig.~\ref{fig:metal_evolution}, we give the metal mass loading factor for our galaxy over time, at the same radii as in Fig.~\ref{fig:mass_outflow}. The parameter used to quantify metal outflow efficiencies varies among works. Here, we define the metal mass loading factor as the metal outflow rate divided by the metal production rate, or
\begin{equation} \label{eq:eta-metal}
\eta_{\rm metal} = \frac{\dot{M}_{\rm metal}}{\rm{SFR} \times (M_{\rm metal}/M_{*})},
\end{equation}
where $\dot{M}_{\rm metal}$ is the metal mass outflow rate, $M_{\rm metal}$ is the total mass in metals produced, and $M_{*}$ is the total mass in stars. We note the very large loading factors in the first 20~Myr are artificial, and a byproduct of the initial conditions. For half of the evolution, the inner three radii give $\eta_{\rm metal}$ below unity (around 0.6), but it increases at each radius, fluctuating around unity for the second half of the simulation. Recent simulations of outflows from a Milky Way type disk indicate typical $\eta_{\rm metal}$ comparable to our results, usually between 0.5 and 1 \citep{Li2017,Fielding2017}. \cite{Muratov2017} computes a slightly different quantity for their galaxies, the normalized metal outflow rate $\eta_{Z} = \dot{M}_{\rm metal}/{\rm SFR}$, finding values of about 0.02 at 0.25~$R_{\rm vir}$ regardless of galaxy circular velocity. Our galaxy is consistent with this value, with an average $\eta_Z = 0.015$, fluctuating between 0.007 and 0.02.

@@

\subsubsection{Differential Mixing of Elements Within the ISM}
%mm3 \textbf{CHANGE: Simplified plot to just log(N/O) to make this less confusing and easier to interpret. Cleaned up text accordingly.}
It is important to understand how metals from each source of stellar yields enrich the ISM. Observations of more massive dwarf galaxies than those simulated here indicate fairly uniform radial gas-phase metallicity profiles, even beyond the stellar radius \citep[e.g.][]{Werk2011,Belfiore2017}. This requires that metal mixing and transport occur on hundred megayear timescales, much more rapidly than the gigayear timescale expected from assuming transport at the cold gas sound speed. Therefore, either metals are transported first through a hot phase with high sound speed, or through efficient turbulent mixing within the ISM \citep[e.g.][]{Avillez2002,Tassis2008,YangKrumholz2012}. It remains uncertain how metal abundances vary in detail within these galaxies, beyond one-dimensional radial profiles, and whether or not abundance distributions depend on the metal species. It is even more unclear how metals are transported and distributed within ultrafaint dwarf galaxies, which generally host too few \ion{H}{2} regions for a detailed examination.

@@

We demonstrate the power of our simulations, which capture a realistic ISM at high resolution with multiple feedback sources, by addressing these questions in Fig~\ref{fig:metal_slices}. The left panel gives the abundance ratio of N to O throughout the ISM. The 
%mm3 left 
   right 
two panels give the slices of number density (top right) and temperature (bottom right) in the mid-plane of a portion of our dwarf galaxy. These 
%mm3 serve to guide the eye in the right panel, clearly indicating 
    show
regions with dense, cold gas clouds ($n \sim 100~\rm{cm}^{-2}$, $T \lesssim 100~$K), warm, diffuse gas ($n\sim 0.1$~cm$^{-3}$, $T\sim 10^{4}$~K), and hot gas from a recent SN explosion ($T\sim10^{6}$~K).

@@

The 
%mm3 [redundant with end of previous para?] number density and temperature panels clearly show a multi-phase ISM: the 
CNM consists of cold filaments that connect dense clumps of molecular gas that are readily visible in both diagrams. Distinguishing the WNM and WIM is difficult, but the lower density regions between the cold filaments are dominated by these phases. Gas from a recent SN explosion is clearly visible as the hot (T~$\gtrsim 10^{6}$~K), diffuse region in the top left corner. As shown in the left panel, log(N/O) varies significantly over this section of the ISM with notable differences across the various phases and ISM structures. As expected, O is overabundant throughout the ISM, most strongly in the region of recent SN enrichment (top left, dark purple region in log(N/O) / dark red in temperature). However, the relative abundance of N increases significantly in the warmer phases, reaching equipartition (white color in log(N/O)) in many patches throughout the ISM. There are three regions in particular that are overabundant in N (green color). 
%mm3 [moved to next para] These are sites of recent AGB winds that have yet to mix with the rest of the ISM.

@@

At our adopted metallicity, nitrogen is predominantly produced in AGB star winds, with very little production in core collapse SNe and winds from more massive stars. Therefore, nitrogen is injected into the ISM with significantly less energy ($v \sim 10$~km~s$^{-1}$) than elements produced in SNe, like oxygen, ($v\sim 10^3$~km~s$^{-1}$). Given the variations in Figure~\ref{fig:metal_slices}, the energetic differences between injection sources can drive abundance variations within the ISM of our dwarf galaxy. 
%mm3
    The regions most rich in N are sites of recent AGB winds that have yet to mix with the rest of the ISM.  
This suggests that metal mixing within the ISM (and also metal ejection from the ISM) is species dependent. A more detailed analysis is beyond the scope of this work, but we plan to investigate this point, and potential observational consequences for stellar abundances, in future work. 
% reference my other paper if it is ready-ish by the time I submit this one.
